A Catalogue of Twists of Supersymmetric Gauge Theories

### 2020-01-21 paper.tex

\subsubsection{Generalized Hodge theory}
Generalized BF theories can be naturally deformed to theories which are perturbatively trivial, but which arise as shadows of non-trivial non-perturbative theories.  These will often appear as topological twists of supersymmetric field theories, the most famous example being the 2d A-model \chris{refer also to the introduction}. By a deformation we will mean a $\CC[t]$-family of classical BV theories which reduce to the given theory at $t=0$.

@@

\subsection{\texorpdfstring{$\cN=(1, 0)$}{N=(1, 0)} Super Yang--Mills}

@@

\vspace{-10pt}
\paragraph{Fields:} The BRST fields are given by:
\begin{itemize}
\item A gauge field $A \in \Omega^1(M;\fg)$.
\item Gauge fermion $\lambda \in \Omega^0(M; \Pi S_+ \otimes W_+ \otimes \fg)$. 
\item Matter boson $\phi\in\Omega^0(M; W_+\otimes U)$.
\item Matter fermion $\psi\in\Omega^0(M; \Pi S_-\otimes U)$.
\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
\end{itemize}

@@

\vspace{-10pt}
\paragraph{Fields:} The BRST fields are given by:
\begin{itemize}
\item Gauge fields $A_{1, 0} \in \Omega^{1, 0}(M; \fg)$, $A_{0, 1}\in\Omega^{0, 1}(M; \fg)$.
\item Gauge fermions $\chi\in\Omega^0(M; \Pi\fg)$, $\xi\in\Omega^{3, 0}(M; \Pi\fg)$, $B\in\Omega^{0, 2}(M; \Pi\fg)$, $\rho\in\Omega^{1, 0}(M; \Pi\fg)$.
\item Matter bosons $\nu\in\Omega^0(M; U\otimes K^{-1/2})$, $\phi\in\Omega^0(M; U\otimes K^{1/2})$.
\item Matter fermions $\psi\in \Omega^{1, 0}(M; \Pi U\otimes K^{1/2})$, $\wt\nu\in\Omega^0(M; \Pi U\otimes K^{-1/2})$.
\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
\end{itemize}

@@

Using Corollary \ref{Kahler_YM_term_cor}, the BV action $S_{\mr{BV}}$ of the $Q$-twisted theory consists of the sum of the following terms:
\begin{align*}
S_{\gauge} &= \int \dvol \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \\
&\qquad + \frac 12 \left( \omega(B \wedge \dd_{A_{1,0}} \rho) + \omega^2\chi\Lambda(\ol \dd_{A_{0,1}} \rho) - \omega(\rho \wedge \dd_{A_{1,0}} B) + \xi \ol \dd_{A_{0,1}} B \right)  \\
S_{\matter} &= \int \bigg( \dvol ((\dd_{A_{1,0}}\nu, \ol \dd_{A_{0,1}} \phi) + (\dd_{A_{1,0}}\phi, \ol \dd_{A_{0,1}} \nu)) + 2\omega^2\wedge(\wt\nu \ol \dd_{A_{1,0}} \psi) + \psi \wedge \ol \dd_{A_{0,1}} \psi + \\
&\qquad + 2\dvol(([\xi,\nu],\wt\nu) + ([\chi, \phi], \wt\nu) )   \bigg) \\
S_{\mr{anti}} &= \int \dd_{A_{1, 0}} c \wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [B, c]\wedge B^* +  [\xi, c]\wedge \xi^* + [\chi, c]\chi^* +[\rho, c]\wedge \rho^* + \\
&\qquad + \frac{1}{2}[c, c]c^* + [\nu, c]\wedge \nu^* + [\phi, c]\wedge \phi^* + [\psi, c]\wedge \psi^* + [\wt\nu, c]\wedge \wt\nu^* \\
I^{(1)}_{\gauge} &=  \int \dvol \left( - (\rho, A_{1,0}^*) + \frac 12 (F_{0,2},B^*) + \frac 12 (F_{1,1}, \chi^*)  \right)\\
I^{(1)}_{\matter} &=  \int \dvol \left( (\wt\nu, \nu^*) + \frac 12( \ol \dd_{A_{0,1}} \phi, \psi^*) \right)\\
I^{(2)}_{\gauge} &= -\frac{1}{4}\int \dvol (\chi^*)^2.
\end{align*}

\begin{thm}
The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills on $M=\RR^6$ with matter valued in a $\fg$-representation $U$ is perturbatively equivalent to the holomorphic Chern--Simons theory on $M\cong \CC^3$ with the space of fields $\map(M, U\ham \fg)$. Moreover, the equivalence is $\MU(3)$-equivariant.
\label{thm:6dholomorphictwist}
\end{thm}
\begin{proof}
The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}. First, we eliminate the fields $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}.  We then observe that the action includes the terms $\int \dvol  (\rho, A_{1,0}^*)$ and $\int \dvol (\wt\nu, \nu^*)$.  In other words, the pairs $(\rho, A_{1,0})$ and $(\nu, \wt\nu)$ form trivial BRST doublets, which can be eliminated using Proposition \ref{prop:BRSTdoublet}. The twisted theory is therefore perturbatively equivalent to the theory with the BV action 
\begin{align*}
 S_{\mr{BV}} &= \int \xi \ol \dd_{A_{0,1}} B  + \psi \wedge \ol \dd_{A_{0,1}} \psi \\
 &+ \dvol\left(\frac 12 (F_{0,2}, B^*) + \frac 12 (\ol \dd_{A_{0,1}} \phi, \psi^*) +  (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([B, c], B^*) + ([\xi, c], \xi^*) + \frac{1}{2}[c, c]c^* +  [\phi, c] \phi^* + ([\psi, c],\psi^*)\right).
\end{align*}
Up to rescaling of the antifields, this is the action functional of the required theory.
\end{proof}

If $U=T^*R=R\oplus R^*$, the R-symmetry group is enhanced to $G_R=\SU(2)\times \U(1)$. We have a homomorphism $\alpha\colon \U(1)\hookrightarrow G_R=\SU(2)\times \U(1)$ given by the diagonal embedding which is compatible with the holomorphic supercharge. We may also use a different twisting homomorphism
\[\phi\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\xrightarrow{\alpha} G_R.\]

@@

\subsection{\texorpdfstring{$\cN=(1, 1)$}{N=(1, 1)} Super Yang--Mills}

@@

\begin{theorem} \label{5d_holo_twist_theorem}
The minimal twist of 5d $\mc N=1$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$, on the product of a Calabi-Yau surface $S$ and an oriented 1-manifold $L$ is equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(S \times L_{\mr{dR}}, U\ham G)$.
\end{theorem}

@@

\subsection{\texorpdfstring{$\cN=1$}{N=1} with chiral multiplet matter} \label{4d_1_section}
We consider $\cN=1$ supersymmetric Yang-Mills for a Lie algebra $\fg$ coupled to supersymmetric matter.
The matter consists of the $\cN=1$ chiral multiplet valued in a complex representation $R$.

@@

The R-symmetry group is $U(1)$ which acts by $\pm 1$ on $\lambda_{\pm}$ and $\mp 1$ on $\psi_{\pm}$.

@@

There is a single non-zero equivalence class of square-zero supercharges in $4$-dimensional $\mc N = 1$, which we fix from here on.
Such supercharges are necessarily of rank $1$, and for concreteness we will fix a square-zero supercharge of negative chirality $$Q = Q_+ \in S_+$$ to twist by. 
Such supercharges are minimal (i.e. have two dimensional image).  
The twisted theory by such a supercharge can always be made $\ZZ$-graded where the twisting datum is given by the identity map $\alpha = {\rm id} : U(1) \to U(1)$. 
Such a $Q$ is preserved under a twisting homomorphism
\[
\MU(2) \to {\rm Spin}(4) \times U(1) 
\]
where on the first component is the map $\MU(2) \to {\rm Spin}(4)$ lifting $\U(2) \to \SO(4)$ and on the second component $\MU(2) \to U(1)$ is the square root of determinant.

We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to $\MU(2)$.
The fields decompose as:
\[
\begin{array} {lllcccccc}
& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
c & \mapsto & A_{0} \in \Omega^0(\CC^2 ; \fg) & -1 & 0 & -1 \\
A & \mapsto & A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) & 0 & 0 & 0 \\
\lambda_- & \mapsto & \lambda_{1,0} \in \Omega^{1,0}(\CC^2 ; \fg) & 0 & -1 & -1 \\
\lambda_+ & \mapsto & \lambda_0 + A_{0,2} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{0,2}(\CC^2 ; \fg) & 0 & +1 & + 1 \\
\phi & \mapsto & \phi \in \Omega^0 (\CC^2 ; R^*) & 0 & 0 & 0 \\
\Bar{\phi} & \mapsto & \gamma_0 \in \Omega^{0,0}(\CC^2 ; R) & 0 & 0 & 0 \\
\psi_+ & \mapsto & \psi_0 + \beta_{2,0} \in \Omega^{0}(\CC^2 ; R^*) \oplus \Omega^{2,0}(\CC^2 ; R^*) & 0 & -1 & -1 \\
\psi_- & \mapsto & \gamma_{0,1} \in \Omega^{0,1}(\CC^2 ; R) & 0 & +1 & +1 
\end{array}
\]
\brian{Is it necessary to put in the antifields?} 
and their antifields:
\begin{align*}
c^* & \mapsto B_{2,2} \in \Omega^{2,2}(\CC^2 ; \fg) \\
A^* & \mapsto B_{2,1} + A^*_{1,0} \in \Omega^{2,1}(\CC^2;\fg) \oplus \Omega^{1,2}(\CC^2; \fg) \\
\lambda^*_- & \mapsto \lambda_{1,0}^* \in \Omega^{1,2}(\CC^2 ; \fg) \\
\lambda^*_+ & \mapsto \lambda_0^*+ B_{2,0} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{2,0}(\CC^2 ; \fg) \\
\phi^* & \mapsto \phi^* \in \Omega^{2,2}(\CC^2 ; R^*) \\
\Bar{\phi}^* & \mapsto \beta_{2,2} \in \Omega^{2,2} (\CC^2 ; R) \\
\psi^*_+ & \mapsto \psi_{2,2}^* + \gamma_{0,2} \in \Omega^{2,2}(\CC^2 ; R) \oplus \Omega^{0,2}(\CC^2 ; R) \\
\psi^*_- & \mapsto \beta_{2,1} \in \Omega^{2,1}(\CC^2 ; R)
\end{align*}

The untwisted action functionals decompose as follows.

@@

\begin{thm}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ is $\MU(2)$-equivariantly equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$, with classical moduli space $T^*[-1]\mr{Map}(\CC^2, R/\gg)$. 
\end{thm}

@@

\subsection{\texorpdfstring{$\cN=2$}{N=2} Super Yang-Mills with Matter} \label{4d_2_section}

We obtain $\mc N=2$ super Yang-Mills theory on $\RR^4$ by dimensionally reducing $\mc N=(1,0)$ super Yang-Mills from $\RR^6$, or $\mc N=1$ super Yang-Mills from $\RR^5$, with a hypermultiplet valued in a symplectic representation $U$.  In these terms we can describe the BRST fields.

\vspace{-10pt}
\paragraph{Fields:}  We can describe the BRST fields of $\mc N=2$ super Yang-Mills with matter valued in the symplectic representation $U$ by restricting the 5d $\mc N=2$ fields from Section \ref{5d_1_section} to representations of the group $\mr O(4)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item $\gg$-valued Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(\phi_1,\phi_2) \in \Omega^1(\RR^4; \gg \otimes \wedge^2(W))^2$.
 \item $U$-valued bosons: a $W$-valued scalar field $\phi \otimes v \in \Omega^0(\RR^4; W \otimes U)$.
 \item $\gg$-valued fermions: a $W$-valued Dirac spinor $\lambda = (\lambda_+ \otimes u_+, \lambda_-\otimes u_-) \in \Omega^0(\RR^4; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
 \item $U$-valued fermions: a Dirac spinor $\psi = (\psi_+,\psi_-) \in \Omega^0(\RR^4; (S_+\oplus S_-) \otimes U)$.
\end{itemize}

>>>>

\begin{eg}
There is a special case of this  of the ``holomorphic symplectic boson". 
\brian{include this?}
\end{eg}
\subsubsection{Generalized Hodge theory}
Generalized BF theories can be naturally deformed to theories which are perturbatively trivial, but which arise as shadows of non-trivial non-perturbative theories.  These will often appear as topological twists of supersymmetric field theories, the most famous example being the 2d A-model \chris{refer also to the introduction}. By a deformation we will mean a $\CC[t]$-family of classical BV theories which reduce to the given theory at $t=0$.

@@

%Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing. 
%The general theory with $\mc N = (1,0)$ supersymmetry consists of pure super Yang-Mills with Lie algebra $\fg$ coupled to $(1,0)$ matter valued in a symplectic vector space $U$, as in Section \ref{sect:mattermultipletSUSY}. 
%In physics terminology, the matter here is referred to as the $6d$ $\mc N = (1,0)$ hypermultiplet.
%
%The $R$-symmetry group is $G_R = \SU(2)$. \brian{Or do we want it's noncompact form ${\rm Sp}(W_+) = {\rm Sp}(2, \CC)$. }

\subsection{\texorpdfstring{$\cN=(1, 0)$}{N=(1, 0)} Super Yang--Mills Theory}

@@

%\vspace{-10pt}
%\paragraph{Fields:} The BRST fields are given by:
%>>>>>>> 016a15254e190191104552713b6e9bc2dba88afb
%\begin{itemize}
%\item A gauge field $A \in \Omega^1(M;\fg)$.
%\item Gauge fermion $\lambda \in \Omega^0(M; \Pi S_+ \otimes W_+ \otimes \fg)$. 
%\item Matter boson $\phi\in\Omega^0(M; W_+\otimes U)$.
%\item Matter fermion $\psi\in\Omega^0(M; \Pi S_-\otimes U)$.
%\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
%\end{itemize}
%
%<<<<<<< HEAD
%Under the $R$-symmetry $\lambda, \phi$ transform as the fundamental representations. \brian{Does this sound right?}

%\subsubsection{Holomorphic twist}
%
%Choose a polarized basis $W_+ = {\rm span}_{\CC}\{w_1, w_2\}$.
%The only square-zero supercharges in the $\mc N=(1,0)$ supersymmetry algebra have rank one.  
%Without loss of generality we will twist with respect to a supercharge of the form 
%\[
%Q = q_+ \otimes w_1 \in S_+ \otimes W_+ .
%\]
%Such a $Q$ is preserved under the twisting homomorphism
%\[
%\MU(3) \to {\rm Spin}(6) \times \SU(2) .
%\]
%In the first component this is the homomorphism $\MU(3) \to {\rm Spin}(6)$ lifting $\U(3) \to {\rm SO}(6)$. 
%In the second component, this is the composition $\MU(3) \to \U(1) \to \SU(2)$ where the first map is $\det^{-1/2}$ and the second map is $z \mapsto \begin{pmatrix} z & 0 \\ 0 & \Bar{z} \end{pmatrix}$. 
%
%There is no twisting datum homomorphism $\alpha : U(1) \to \SU(2)$ compatible with this twisting homomorphism.
%Thus, the resulting twisted theory is only $\ZZ/2$-graded.
%
%Under the action of $\MU(3)$, the fields decompose as:
%\begin{align*}
%c & \mapsto A_0 \in \Omega^{0,0}(\CC^3 ; \fg) \\
%A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^3 ; \fg) \oplus \Omega^{1,0}(\CC^3 ; \fg) \\
%\lambda & \mapsto \lambda_{0} + {B}_{1,0} + \chi + \lambda_0 \in \Omega^0(\CC^3 ; \fg) \oplus \Omega^{0,2}(\CC^3 ; \fg) \oplus \Omega^{3,0}(\CC^3 ; \fg) \oplus \Omega^{3,2}(\CC^3 ; \fg) \\
%\phi & \mapsto \nu + \psi_0 \in \Omega^0(\CC^3; K^{-1/2} \otimes U) \oplus \Omega^0(\CC^3 ; K^{1/2} \otimes U) \\
%\psi & \mapsto \psi_{0,1} + \nu' \in \Omega^{0,1}(\CC^3; K^{1/2} \otimes U) \oplus \Omega^{0,3} (\CC^3; K^{1/2} \otimes U ),
%\end{align*} 
%
%%\begin{align*}
%%c & \mapsto A_0 \in \Omega^{0,0}(\CC^3 ; \fg) \\
%%A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^3 ; \fg) \oplus \Omega^{1,0}(\CC^3) \\
%%\lambda & \mapsto \lambda_{0,2} w_1 + {B}_{1,0}w_2 + \chi w_1 + \lambda_0 w_2 \in \Omega^{0,2}(\CC^3 ; W_+ \otimes \fg) \oplus \Omega^{0}(\CC^3 ; W_+ \otimes \fg) \\
%%\phi & \mapsto \nu w_1 + \psi_0 w_2 \in \Omega^0(\CC^3; W_+ \otimes U) \\
%%\psi & \mapsto \psi_{0,1} + \nu' \in \Omega^{0,1}(\CC^3; U) \oplus \Omega^0(\CC^3; U),
%%\end{align*} 
%
%\brian{only complaint is the use of $\psi_0$. Maybe use a different letter since $\psi$ is used for the fermion.}
%and similarly with the anti-fields, where the fields $A_{\bu, \bu}$, $\lambda_{\bu,\bu}$ are $\fg$-valued differential forms, and the fields $\psi_{\bu,\bu}$ are $U$-valued differential forms.  In terms of these fields, and using Corollary \ref{Kahler_YM_term_cor}, the BV action $S_{\mr{BV}}$ of the $Q$-twisted theory will consist of the sum of the following terms.
%=======
\subsubsection{Holomorphic twist}
\label{sec:6dholomorphictwist}

@@

\vspace{-10pt}
\paragraph{Fields:} The BRST fields are given by:
\begin{itemize}
\item Gauge fields $A_{1, 0} \in \Omega^{1, 0}(M; \fg)$, $A_{0, 1}\in\Omega^{0, 1}(M; \fg)$.
\item Gauge fermions $\chi\in\Omega^0(M; \Pi\fg)$, $\xi\in\Omega^{3, 0}(M; \Pi\fg)$, $B\in\Omega^{0, 2}(M; \Pi\fg)$, $\rho\in\Omega^{1, 0}(M; \Pi\fg)$.
\item Matter bosons $\nu\in\Omega^0(M; U\otimes K^{-1/2})$, $\phi\in\Omega^0(M; U\otimes K^{1/2})$.
\item Matter bosons $\nu\in\Omega^{3,0}(M; U)$, $\phi\in\Omega^0(M; U)$.
\item Matter fermions $\psi\in \Omega^{1, 0}(M; \Pi U\otimes K^{1/2})$, $\wt\nu\in\Omega^0(M; \Pi U\otimes K^{-1/2})$\brian{Should this be $\psi \in \Omega^{0,1}(M; \Pi U\otimes K^{1/2})$?}.
\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
\end{itemize}

@@

Using Corollary \ref{Kahler_YM_term_cor}, the BV action $S_{\mr{BV}}$ of the $Q$-twisted theory consists of the sum of the following terms:

\begin{align*}
S_{\gauge} &= \int \dvol \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \\
&\qquad + \frac 12 \left( \omega(B \wedge \dd_{A_{1,0}} \rho) + \omega^2\chi\Lambda(\ol \dd_{A_{0,1}} \rho) - \omega(\rho \wedge \dd_{A_{1,0}} B) + \xi \ol \dd_{A_{0,1}} B \right)  \\
S_{\matter} &= \int \bigg( \dvol ((\dd_{A_{1,0}}\nu, \ol \dd_{A_{0,1}} \phi) + (\dd_{A_{1,0}}\phi, \ol \dd_{A_{0,1}} \nu)) + 2\omega^2\wedge(\wt\nu \ol \dd_{A_{1,0}} \psi) + \psi \wedge \ol \dd_{A_{0,1}} \psi + \\
&\qquad + 2\dvol(([\xi,\nu],\wt\nu) + ([\chi, \phi], \wt\nu) )   \bigg) \\
S_{\mr{anti}} &= \int \dd_{A_{1, 0}} c \wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [B, c]\wedge B^* +  [\xi, c]\wedge \xi^* + [\chi, c]\chi^* +[\rho, c]\wedge \rho^* + \\
&\qquad + \frac{1}{2}[c, c]c^* + [\nu, c]\wedge \nu^* + [\phi, c]\wedge \phi^* + [\psi, c]\wedge \psi^* + [\wt\nu, c]\wedge \wt\nu^* \\
I^{(1)}_{\gauge} &=  \int \dvol \left( - (\rho, A_{1,0}^*) + \frac 12 (F_{0,2},B^*) + \frac 12 (F_{1,1}, \chi^*)  \right)\\
I^{(1)}_{\matter} &=  \int \dvol \left( (\wt\nu, \nu^*) + \frac 12( \ol \dd_{A_{0,1}} \phi, \psi^*) \right)\\
I^{(2)}_{\gauge} &= -\frac{1}{4}\int \dvol (\chi^*)^2.
\end{align*}

\begin{thm}
The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills on $M=\RR^6$ with matter valued in a $\fg$-representation $U$ is perturbatively equivalent to the holomorphic Chern--Simons theory on $M\cong \CC^3$ with the space of fields $\map(M, U\ham \fg)$. Moreover, the equivalence is $\MU(3)$-equivariant.
\label{thm:6dholomorphictwist}
\end{thm}
\brian{What's our convention for ``twisted maps?}

\begin{proof}
The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}. First, we eliminate the fields $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}.  We then observe that the action includes the terms $\int \dvol  (\rho, A_{1,0}^*)$ and $\int \dvol (\wt\nu, \nu^*)$.  In other words, the pairs $(\rho, A_{1,0})$ and $(\nu, \wt\nu)$ form trivial BRST doublets, which can be eliminated using Proposition \ref{prop:BRSTdoublet}. The twisted theory is therefore perturbatively equivalent to the theory with the BV action 
\begin{align*}
 S_{\mr{BV}} &= \int \xi \ol \dd_{A_{0,1}} B  + \psi \wedge \ol \dd_{A_{0,1}} \psi \\
 &+ \dvol\left(\frac 12 (F_{0,2}, B^*) + \frac 12 (\ol \dd_{A_{0,1}} \phi, \psi^*) +  (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([B, c], B^*) + ([\xi, c], \xi^*) + \frac{1}{2}[c, c]c^* +  [\phi, c] \phi^* + ([\psi, c],\psi^*)\right).
\end{align*}
Up to rescaling of the antifields, this is the action functional of the required theory.
%where $A_{0,\bu} = c + A_{0,1} + B + \xi^*$ and $B_{3, \bu} = \xi + B^* + A_{0,1}^*+ c^*$. 
\end{proof}

If $U=T^*R=R\oplus R^*$, the R-symmetry group is enhanced to $G_R=\SU(2)\times \U(1)$. We have a homomorphism $\alpha\colon \U(1)\hookrightarrow G_R=\SU(2)\times \U(1)$ given by the diagonal embedding which is compatible with the holomorphic supercharge. We may also use a different twisting homomorphism
\[\Tilde{\phi}\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\xrightarrow{\alpha} G_R.\]

@@

@@

\begin{theorem} \label{thm: 5dholtwist}
The minimal twist of 5d $\mc N=1$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$, on the product of a Calabi-Yau surface $S$ and an oriented 1-manifold $L$ is equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(S \times L_{\mr{dR}}, U\ham G)$.
\end{theorem}

@@

The 4-dimensional supersymmetry algebra has odd part $\Sigma\cong S_+\otimes W\oplus S_-\otimes W^*$, where $S_+, S_-$ are the 2-dimensional spin representations of $\Spin(4, \CC)\cong \SU(2) \times \SU(2)$ and $W$ is a complex vector space. 
We have isomorphisms $S_\pm \cong S_\pm^*$ which equivalently determine equivariant pairings $S_\pm \otimes S_\pm \to \CC$.

There are Yang--Mills theories with $\cN=1,2,4$ supersymmetry, which we consider separately.

\subsection{\texorpdfstring{$\cN=1$}{N=1} Super Yang-Mills theory} \label{4d_1_section}
We consider $\cN=1$ supersymmetric Yang-Mills for a Lie algebra $\fg$ coupled to supersymmetric matter.
The matter consists of the $\cN=1$ chiral multiplet valued in a complex representation $R$.

The general setup for $\cN=1$ super Yang--Mills is described in Section \ref{sec:SYM} which we now recall. 
Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing and $R$ a complex $\fg$-representation. 
We consider $\cN=1$ super Yang--Mills theory on $M=\RR^6$ with the Euclidean metric. 
We fix $W=\CC$. 
The theory admits an $R$-symmetry group $G_R=\U(1)$.

This theory admits a unique twist, which is necessarily of rank $1$:
\begin{itemize}
\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 2 invariant directions, so it gives rise to a holomorphic theory. 
The identity homomorphism $\alpha = {\rm id} \colon \U(1)\rightarrow \U(1)$ given by the identity, makes $Q$ weight $+1$, so in this case we get a $\ZZ$-grading. 
Such a supercharge is stabilized by $G=\SU(2)$. 
Also, we have a compatible twisting homomorphism 
\[
\phi : \MU(2) \to {\rm Spin}(4) \times U(1) 
\]
where on the first component is the map $\MU(2) \to {\rm Spin}(4)$ lifting $\U(2) \to \SO(4)$ and on the second component $\MU(2) \to U(1)$ is the square root of determinant. 
\end{itemize}

@@

@@

For concreteness, we will fix a square-zero supercharge of positive chirality
\[
Q = Q_+ \in S_+ \otimes W
\]
to twist by. 
The data of such a $Q_+$ is equivalent to the data of a K\"{a}hler structure $L$ on $V_\RR$.

Under the embedding $\MU(L) = \MU(2) \subset \Spin(\VV_\RR)$, the spin representations decompose as
\[
S_+ = \det(L)^{-1/2} \oplus \det(L)^{1/2} \;\; , \;\; S_- = L \otimes \det(L)^{-1/2} .
\]
Moreover, under the twisting homomorphism
\[
\phi = \det \, ^{1/2} : \MU(2) \to \U(1)
\]
we have an identification $W = \det(L)^{1/2}$. 
By construction, $Q_+$ lies in the first factor of $S_+ \otimes W = \CC \oplus \det(L)$.

We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to $\MU(2)$.
The fields decompose as:
\[
\begin{array} {lllcccccc}
& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
c & \mapsto & A_{0} \in \Omega^0(\CC^2 ; \fg) & -1 & 0 & -1 \\
A & \mapsto & A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) & 0 & 0 & 0 \\
\lambda_- & \mapsto & \lambda_{1,0} \in \Omega^{1,0}(\CC^2 ; \fg) & 0 & -1 & -1 \\
\lambda_+ & \mapsto & \lambda_0 + A_{0,2} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{0,2}(\CC^2 ; \fg) & 0 & +1 & + 1 \\
\phi & \mapsto & \phi \in \Omega^0 (\CC^2 ; R^*) & 0 & 0 & 0 \\
\Bar{\phi} & \mapsto & \gamma_0 \in \Omega^{0,0}(\CC^2 ; R) & 0 & 0 & 0 \\
\psi_+ & \mapsto & \psi_0 + \beta_{2,0} \in \Omega^{0}(\CC^2 ; R^*) \oplus \Omega^{2,0}(\CC^2 ; R^*) & 0 & -1 & -1 \\
\psi_- & \mapsto & \gamma_{0,1} \in \Omega^{0,1}(\CC^2 ; R) & 0 & +1 & +1 
\end{array}
\]
The anti-fields decompose similarly. 
%\brian{Is it necessary to put in the antifields?} 
%and their antifields:
%\begin{align*}
%c^* & \mapsto B_{2,2} \in \Omega^{2,2}(\CC^2 ; \fg) \\
%A^* & \mapsto B_{2,1} + A^*_{1,0} \in \Omega^{2,1}(\CC^2;\fg) \oplus \Omega^{1,2}(\CC^2; \fg) \\
%\lambda^*_- & \mapsto \lambda_{1,0}^* \in \Omega^{1,2}(\CC^2 ; \fg) \\
%\lambda^*_+ & \mapsto \lambda_0^*+ B_{2,0} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{2,0}(\CC^2 ; \fg) \\
%\phi^* & \mapsto \phi^* \in \Omega^{2,2}(\CC^2 ; R^*) \\
%\Bar{\phi}^* & \mapsto \beta_{2,2} \in \Omega^{2,2} (\CC^2 ; R) \\
%\psi^*_+ & \mapsto \psi_{2,2}^* + \gamma_{0,2} \in \Omega^{2,2}(\CC^2 ; R) \oplus \Omega^{0,2}(\CC^2 ; R) \\
%\psi^*_- & \mapsto \beta_{2,1} \in \Omega^{2,1}(\CC^2 ; R)
%\end{align*}

Let $\omega\in\Omega^{1, 1}(M)$ be the K\"ahler form, $\Omega\in\Omega^{2, 0}(M)$ the holomorphic volume form and $\ol{\Omega}\in\Omega^{0, 2}(M)$ the antiholomorphic volume form.  We denote the real volume form on $M$ by
\[\dvol = \frac{\omega^2}{2} = \Omega\wedge \ol{\Omega}.\]

Using Corollary \ref{Kahler_YM_term_cor}, the BV action $S_{\mr{BV}}$ of the $Q$-twisted theory consists of the sum of the following terms:

@@

Notice that a priori the theory is only $\MU(2)$-equivariant, but manifestly descends to a $\U(2)$-equivariant theory.

\begin{thm}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ is $\U(2)$-equivariantly equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$, with classical moduli space $T^*[-1]\mr{Map}(\CC^2, R/\gg)$. 
\end{thm}

@@

\subsection{\texorpdfstring{$\cN=2$}{N=2} Super Yang-Mills Theory} \label{4d_2_section}

The general setup for $\cN=2$ super Yang-Mills is described in Section \ref{sec:SYM} which we now recal.
Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear nondegenerate invariant pairing and $U$ a complex symplectic $\fg$-representation. 
We consider $\cN=2$ super Yang-Mills theory on $M = \RR^4$ with the Euclidean metric. 
We fix $W=\CC^2$. The $R$-symmetry group depends on the type of the representation $U$:
\begin{itemize}
\item The theory admits an $R$-symmetry group $G_R=\U(2)$ with $W$ the two-dimensional defining representation.
%\item If $U = T^* R=R\oplus R^*$ for a $\fg$-representation $R$, then the theory admits an $R$-symmetry group $G_R=\U(2)\times \U(1)$, where $\U(1)$ acts trivially on $W$, with weight $1$ on $R$ and with weight $-1$ on $R^*$.
\end{itemize}

\paragraph{Twisting data:}
There are three classes of square-zero supercharge in the 4d $\mc N=2$ supersymmetry algebra, distinguished by the ranks of the two summands $(Q_+,Q_-) \in S_+ \otimes W \oplus S_- \otimes W^*$.
\begin{itemize}
 \item[1.] Rank $(1,0)$ and $(0,1)$ supercharges automatically square to zero.  
 The corresponding twists are holomorphic.
 Such twists factor through a copy of the $\cN = 1$ supersymmetry algebra.
 \item[2.] Rank $(2,0)$ and $(0,2)$ supercharges also automatically square to zero. 
 The corresponding twists are topological (the \emph{Donaldson twist}).
 \item[3.] Rank $(1,1)$ square-zero supercharges have three invariant directions.
\end{itemize}

\subsubsection{Holomorphic twist}
\label{sect:4d_2_holomorphictwist}

Take a nonzero square-zero rank $(1,0)$ supercharge $Q\in S_+ \otimes W$.
We choose a basis for $W$ given by $\{w_1,w_2\}$, and for concreteness we take $Q=q_+ \otimes w_1$ for some nonzero vector $q_+ \in S_+$. 
Such a $Q$ is automatically holomorphic and the choice of $Q$ is equivalent to the data of a K\"ahler structure $L$ on $V_\RR$ together with a complex half-density on $L$.

Under the embedding $\MU(L) \subset \Spin(V_\RR)$, the $S_+$ splits as
\[
S_+ = \det(L)^{-1/2} \oplus \det(L)^{1/2} \;\; , \;\; S_- = L \otimes \det(L)^{-1/2} .
\]
